Order is half of life -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-12-15 paper/paper-mainfile.tex
some changes

Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
after every refinement of c but after at least one:
$$ \PossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
$$ \PossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
if $E(c) \neq \emptyset$ and  $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.

The set of executability-enabling states of c is
$E(c) = \{s \in 2F  \mid  \exists$ t.o. refinement of $c$ applicable in $s \}$.
The set of resulting states of c w.r.t. some state $s \in 2^F$ is
$R_s(c) = \{s' \in 2^F | \exists$ t.o. refinement appl. in $s$ res. in $s' \}$.

So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.

Then, the precondition-relaxed effects $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
This means $\RelPossEffPlus$ and $\RelPossEffMinus$ has every effect that $\PossEffPlus$ and $\PossEffMinus$  do, respectively. But
the precondition relaxation can make further refinements executable that produce
effects that can not be achieved in the non-relaxed domain. 
In other words, we can calculate a super-set, that might contain some false candidates, of the real preconditions and effects that might occur after any execution of $c$, i.e.\  $\PossEffMinus \subseteq \RelPossEffMinus$, and $\PossEffPlus  \subseteq \RelPossEffPlus$.

\emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement. So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.

A fact $f \in F$ is an \emph{executability-relaxed precondition} of $c$ if and only if for all t.o. refinements (ignoring executability of the refinement) $\langle a_0 ... a_n \rangle$ of $c$ there exists an action $a_i$ with $f \in \prec(a_i)$ and there does not exist an action $a_j$ with $j < i$ and $f \in add(a_j)$, where $i, j \in \{0, ..., n\}$.

There exists a polynomial-time algorithm for inferring the executability-relaxed preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
In this paper, we will be utilising both of these, as seen in the next section.
%the precondition-relaxed possible effects, which may hold after at least one refinement of c.

>>>>

% Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
% after every refinement of c but after at least one:
% $$ \PossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
% $$ \PossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
% if $E(c) \neq \emptyset$ and  $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.

% The set of executability-enabling states of c is
% $E(c) = \{s \in 2F  \mid  \exists$ t.o. refinement of $c$ applicable in $s \}$.
% The set of resulting states of c w.r.t. some state $s \in 2^F$ is
% $R_s(c) = \{s' \in 2^F | \exists$ t.o. refinement appl. in $s$ res. in $s' \}$.

% So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
% with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.

% Then, the precondition-relaxed effects $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
% This means $\RelPossEffPlus$ and $\RelPossEffMinus$ has every effect that $\PossEffPlus$ and $\PossEffMinus$  do, respectively. But
% the precondition relaxation can make further refinements executable that produce
% effects that can not be achieved in the non-relaxed domain. 
% In other words, we can calculate a super-set, that might contain some false candidates, of the real preconditions and effects that might occur after any execution of $c$, i.e.\  $\PossEffMinus \subseteq \RelPossEffMinus$, and $\PossEffPlus  \subseteq \RelPossEffPlus$.

% \emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement. So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
% if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.

% A fact $f \in F$ is an \emph{executability-relaxed precondition} of $c$ if and only if for all t.o. refinements (ignoring executability of the refinement) $\langle a_0 ... a_n \rangle$ of $c$ there exists an action $a_i$ with $f \in \prec(a_i)$ and there does not exist an action $a_j$ with $j < i$ and $f \in add(a_j)$, where $i, j \in \{0, ..., n\}$.

% There exists a polynomial-time algorithm for inferring the executability-relaxed preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
% In this paper, we will be utilising both of these, as seen in the next section.
%the precondition-relaxed possible effects, which may hold after at least one refinement of c.
